---
title: "Progress Report"
author: "Charles Bond"
date: "11/15/2020"
output: pdf_document
bibliography: refsA.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Current Status: Stuck, cannot run script

I have checked every link, the two githubs and the data repository provided in the **Availability of Materials and Data** section of the article of interest. Looking for the tools to run the PCA analysis shown in figure 2 [@RN44], I have been unable to run the code given due to what seems to be a basic oversight. 

The very first lines of code in the Rscript file for the PCA analysis are as follows:

`source(paste0(Sys.getenv('ROOT_MICROBIOME_DIR'), "/code/hdr.microbiome_methods.R"));
source(paste0(Sys.getenv('ROOT_MICROBIOME_DIR'), "/code/hdr.base_methods.R"));`

No folder labeled "code" appears in either of the provided github repositories, nor can I find R files with the names given here. So, without the associated R files in any repository, I cannot run the code as is. I am trying to wrap my head around running a PCA of what data I have here, but this is a ton of data, of a kind that I've not really worked with before, so I don't know where to start.  


Based on the availability of the data and the posting of the code on github ( https://github.com/bvilhjal/mixmogam and https://github.com/mahort/root_microbiome.
 ) I have selected a paper on the *Arabidopsis* root microbiome [@RN44] as the subject of my next replication attempt. If it goes well there are a lot of figures in this paper that would be worthwhile to replicate, but the one I am mmost interested in is the PCA shown in Figure 2 of the paper. 

Once again, this paper uses the package `vegan` to do the PCA, so I've got that.

## Status: Making progress, found PCA file in github and just trying to figure out where to start.
I am confused on how approach this, like I made a github repository for my replication, but they have a huge github repository for the original, and I'm wondering if I should download files individually or try to pull the whole project down in case there are files it's referncing that I miss?
I downloaded whole github repository as a zip file and put it here, but I guess I need to alter relative paths or something to make it work? I tried running one of the PCA Rscript and get the error
"Error in getData(cutoff = otuCutoff, combined = FALSE, marker = phylogeneticMarker,  : 
  unused arguments (cutoff = otuCutoff, combined = FALSE, marker = phylogeneticMarker, tissue = organ, minReadsPerSite = minimumReads, minSamplePerOTU = 1, whetherToGetTaxa = TRUE, rarefy = (minimumReads > 1), numberOfRarefactions = 1)", 
  which idk what that means but I guess I need to tinker with this more. 

```{r, echo=TRUE}
library(vegan)
```

## References

